---
title: 'Lab 3: Text mining and sentiment analysis'
output: github_document
editor_options: 
  chunk_output_type: console
---
## Text mining

In the second half of this lab, you'll do some basic text mining and sentiment analysis using data from the [Yelp data challenge](https://www.yelp.com/dataset/challenge/winners). Specifically, you'll be looking at reviews for businesses in Charlotte, NC. This file is available in the data folder of this lab repo.

**IMPORTANT**: Yelp has some restrictions on these data, primarily that it cannot be shared publicly or used for publication/analysis. You are free to use it for this lab or for personal research, but you cannot reuse it for other public facing projects. Yelp now has a public version of their data available at [this link](https://www.yelp.com/dataset).

```{r}
library(tidyverse)
library(tidytext)
library(knitr)

yelp_data<-read_csv("data/charlotte_restaurants.csv")
```

These data include multiple variables about businesses listed in Yelp. In this case, only restaurants are included, and there are dummy variables (0/1) for the 10 most common restaurant categories. Here's a list of them and the count of reviews in each:

```{r}
rest_table<-yelp_data %>%
  pivot_longer(`American (New)`:Sandwiches,
               names_to="type",
               values_to="pres") %>%
  group_by(type) %>%
  summarise(count=sum(pres)) %>%
  arrange(-count)

kable(rest_table)
```

**Question 1 (3 points)**: Identify the 20 most common words in these reviews, first filtering out the stopwords using an anti_join as shown in the class script for text mining. You can use the top_n function to select the 20 most common words. Use the arrange function to order your results from highest to lowest as shown in the table above. Use kable to call the table with your results when done.

```{r}
#Code goes here.
```

**Question 2 (2 points)**: Using ggplot, create a bar plot showing the frequency of these most common words. The class script on text mining has an example of how to do this using geom_col. Note that you'll have to use the reorder function (shown in the class script on text mining) to order these bars from high to low values.

```{r}
#Code goes here
```


**Question 3 (5 points)**: Now let's compare two types of restaurants. Filter the dataset so you just have restaurants with *one* or *five* stars based on reviews (see the "stars" variable). Using the same process of question 1, identify the 20 most common words (not counting stop words) in each type of review (one/five star). Use kable to call the head of your table when done.

```{r}
#Code goes here
```


**Question 4 (2 points)**: Looking at your results in question 3, identify *two* notable difference in the words used for one star and five star reviewed restaurants.

{Your response goes here}

**Question 5 (3 points)**: Which burger restaurants had the most positive reviews? Filter the dataset so you only have restaurants classified as Burger (meaning they have a 1 in that column). Tokenize the words used in reviews and join sentiments from the Bing sentiment dictionary. Use group_by and summarise to count the number of positive and negative words by restaurant name. Then make the data wider so that the counts of positive and negative words are separate variables. Call the head of your table when done.*

```{r}
#Code goes here
```

**Question 6 (3 points)**: Use mutate to calculate the percentage of positive and negative words for each restaurant, then filter to select restaurants with at least 1,500 total words. Which restaurant had the highest rate of positive words? Which had the highest negative rate? 

```{r}
#Calculate the rate here
```


{List the two restaurants here.}

**Question 7 (2 points)**: Assess the value of the analysis you did in questions 5 and 6. Do you think this is a valid way to measure restaurant quality? Why or why not? What's one additional improvement you would make to this analysis?

{Your response goes here.}