---
title: 'Geog4/6300: Lab 3'
output:
  github_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
```

## Calculating descriptive statistics

**Due:** Wednesday, Sept. 20

**Value:** 20 points

**Overview:**

This lab is intended to assess your ability to generate basic descriptive statistics. You'll be using monthly weather data from the Daymet climate database (http://daymet.ornl.gov) for all counties in the United States over a 10 year period (2005-2015). These data are available as a part of this repo. You can look back to [Lab 1](https://github.com/jshannon75/geog4300_lab1) for metadata on these variables.

These labs are meant to be done collaboratively, but your final submission should demonstrate your own original thought (don’t just copy your classmate’s work or turn in identical assignments). Your answers to the lab questions should be typed in the provided RMarkdown template. You'll then "knit" this to an HTML document and upload it to your class Github repo.

## Questions 1-3

Your name: {Name goes here}

**Question 1 (2 points)**: Load the tidyverse package and import the data from the data folder of this repo. 

```{r}
#Code goes here.
```


**Question 2 (4 points):** Let's make a very basic climate change model. Create a new variable (tmax_new), that adds two degrees Celsius to the existing maximum temperature for each county. Calculate the mean and standard deviation for the original maximum temperature variable and a new one two degrees higher, grouping these by each census region. Call the table using kable when you are done.

```{r}
#Code goes here.
```

**Question 3 (2 points):** How do the two variables you calculated in question 2 compare? Explain any similarities or differences you find in their means and standard deviations.

```{r}

```

## Questions 4 and 5

**Question 4 (3 points):** Based on scripts used in class, create a data frame that shows the mean, median, standard deviation, CV, and IQR for the _**prcp**_ variable. 

```{r}
#Code goes here
```

**Question 5 (2 points):** Based on the data in question 4, are these data skewed or roughly normal in distribution? Which measures of central tendency and dispersion should you use as a result?*

{Your interpretation goes here.}

## Questions 6-8

**Question 6 (3 points):** Based on scripts used in class, create a box plot graphic that shows the distribution of *vapor pressure* (a metric used for humidity) by region in each year using ggplot. You'll need to use the facet_wrap function to separate regions. 

```{r}
#Code goes here.
```


**Question 7 (2 points):** Identify two notable patterns evident in the box plot, either within or between regions. Explain how these trends are visible in the graphs you created.

{Explanation goes here.}

**Question 8 (2 points):** In plain English, explain each of the functions you used in question 6 along with their parameters. For example, what's included in the aes parentheses and why?

{Explanation goes here.}

## Extra credit!! (2 points)

Create one additional visualization from these data using ggplot that's different from the ones you've done above or in lab 1. In a sentence or two, explain what you think this graphic shows. If you want inspiration, see this page: http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html

```{r}
#Code goes here
```

{Your explanation goes here}

